Response to Reviewer One

### 2021-05-04 Scripts/Manuscript.Rmd
Continue addressing reviewer 1

We estimated the intensity of the distributional shift of transboundary stocks in terms of changes in catch proportion by 2030 (2020-2040) and 2050 (2040-2060), relative to the recent past (1951-2005) (see Methods). Findings show that by 2030, the global average catch proportion of transboundary stocks that are projected to change beyond the EEZ’s historic proportion is 59% ± 17% (Fig. \@ref(fig:toeFigure4)A). Moreover,  85% (n = 239) of the world EEZs would have experienced changes in catch proportion of transboundary stocks by 2030. Changes in catch proportion are expected to become more common and intense slightly towards the mid -21st century at both the stock and EEZ level (Figs. \@ref(fig:toeFigureS3) and \@ref(fig:toeFigureS4)).

>>>>

We estimated the intensity of the distributional shift of transboundary stocks in terms of changes in catch proportion by 2030 (2020-2040) and 2050 (2040-2060), relative to the recent past (1951-2005) (see Methods). Findings show that by 2030, the global average catch proportion of transboundary stocks that are projected to change beyond the EEZ’s historic proportion is 59% ± 17% (Fig. \@ref(fig:toeFigure4)A). Moreover,  85% (n = 239) of the world EEZs would have experienced changes in catch proportion of transboundary stocks by 2030. **There will be an increase in the number of stocks changing their catch proportion and the number of EEZs with changing stocks towards the mid-21st century. Such increase will be followed by an also increase in the intensity of the proportion change (Figs. \@ref(fig:toeFigureS3) and \@ref(fig:toeFigureS4)).**

### 2021-05-04 Scripts/Reviews/reviewer_one.Rmd
Continue addressing reviewer 1

- Response: [Not responded] 
- *Response*: [Draft response here] 
- **Response**: [Response compleded her and in manuscript]

@@

@@

@@

@@

@@

@@

@@

>>>>

- Response: [Not responded] 
- *Response*: [Draft response here] 
- **Response**: [Response completed her and in manuscript]

@@

- **Response:** Thank you for your comment. We provide direction of change in the next figure (Figure 5 of the revised manuscript) showing winners and losers according to neighboring EEZs. Here we show how each neighboring EEZ will stand to win or lose against its neighbors. **NOTE FOR CO-AUTHORS:** *I am hesitant of actually pointing out winners and losers (e.g., stating that Spain will loos most of its catch to France). Hence, I rather leave the results and discussion more general. THoughts?*

@@

- **Response:** We have modified this sentence in the revised manuscript with the hopes to make it less jargon-y. It now reeds on line *7* of *P9* the revised manuscript: "*There will be an increase in the number of stocks changing their catch proportion and the number of EEZs with changing stocks towards the mid-21st century. Such increase will be followed by an also increase in the intensity of the proportion change (Figs. S3 and S4).*"

@@

- **Response:** We realize the figure was missing the legend and color bar making it confusing for the reader. We have now included the legend explaining the legend and color bar.

@@

- *Response:* Thank you for this comment. We have included a couple of examples of management plans that are somehow prepared or have respond to the issues we highlight.

@@

- **Response:** Please see previous comment.

@@

- **Response:** Thank you for your comment. For this paper we used one climate model (the GFDL) forced following one climate change scenario (RCP 8.5) to couple with one species distribution model. For this reason, providing quantitative upper and lower bounds of our results is not possible and would require substantial extra computation. However, because we have 10 different runs of the GFDL we are capable of providing a a less conservative estimate of the numbers you mention (i.e., the number of shifting stocks and EEZs). This was originally presented in the methods section as a sensitivity analyses and has now been moved to the Methods section of the main paper. It reads on line *XXX* of page *XX*: *We also computed a less conservative estimation of shifting transboundary stocks by including a threshold of one standard deviation (i.e., representing a probability of 68% that the stock had shifted from natural variation; see methods). In this case, the global average shift in the shared distribution of transboundary stocks is 2029 $\pm$ 27 years, a difference of about 7 years (Fig. S8). In total, 5,745 transboundary stocks would shift their shared distributions between 2006 and 2100 considering a less conservative metric, that is, 33% (n = 1626) more shifting stocks (Figs. S2 and S8).*

@@

- **Response:** We agree with this comment. However, based on the data available we are unable to increase the detail of our study.
